Output Summary

### 2023-04-05 03-post-process/output-plots-children/13-post-vs-prior.Rmd
Update post_v_prob() plot function
xlim argument was not working

```{r post-v-prior-fn}
# argument list:
# post_samps & prior_samps: samples from their respective PDFs
# post_col & prior_col: (non-transparent) colors for each PDF (will be made transparent for bar fills based on the alpha argument)
# main: plot title
# y_max: maximum bin probability height to display; should be [0,1]
# legend_loc: position of the legend (e.g., "topright")
# n_bins: the number of bins
# alpha: transparency setting for bar fills

post_v_prior = function(post_samps, prior_samps, prior_col = "salmon", post_col = "royalblue",
                        main = NULL, y_max = 0.3, xlim = NULL, legend_loc = NA, n_bins = 50, alpha = 0.5) {

  # get the range of all samples
  rng = range(post_samps, prior_samps)

  # if xlim was provided, take it into consideration when creating breaks
  if (is.null(xlim)) {
    breaks = seq(rng[1], rng[2], length = n_bins)
  } else {
    breaks = seq(min(rng[1], xlim[1]), max(rng[2], xlim[2]), length = n_bins)
  }

  # calculate the data for the histogram
  prior_hist = hist(prior_samps, plot = FALSE, breaks = breaks)
  post_hist = hist(post_samps, plot = FALSE, breaks = breaks)

  # convert bin counts to probabilities
  prior_probs = prior_hist$counts/sum(prior_hist$counts)
  post_probs = post_hist$counts/sum(post_hist$counts)

@@

  # draw segments to connect axes at origin
  usr = par("usr")
  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
  segments(usr[1], usr[3], usr[1], usr[4], xpd = TRUE)

  # add a legend in the desired location if not NULL
  if (!is.na(legend_loc)) {
    legend(legend_loc, legend = c("Prior", "Posterior"), bty = "n", pch = 22, pt.cex = 1.75, cex = 0.8, col = c(prior_col, post_col), pt.bg = scales::alpha(c(prior_col, post_col), 0.5))
  }
}
```

```{r post-v-prior-wrappers}
# wrapper to create plot for all populations
post_v_prior_pops = function(post_param, prior_param, legend_loc = "topright", xlim = NULL, is_rho = FALSE, y_max = 0.3, ...) {

>>>>

```{r post-v-prior-fn}
post_v_prior = function(post_samps, prior_samps, prior_col = "salmon", post_col = "royalblue",
                        main = NULL, y_max = 0.5, xlim = NULL, legend_loc = NA, n_bins = 50, alpha = 0.5) {

  if (!is.null(xlim)) {
    post_samps_keep = post_samps[post_samps >= xlim[1] & post_samps <= xlim[2]]
    prior_samps_keep = prior_samps[prior_samps >= xlim[1] & prior_samps <= xlim[2]]
  } else {
    post_samps_keep = post_samps
    prior_samps_keep = prior_samps
  }
  p_post_keep = length(post_samps_keep)/length(post_samps)
  p_prior_keep = length(prior_samps_keep)/length(prior_samps)

  # get the range of all samples
  rng = range(post_samps_keep, prior_samps_keep)
  if (!is.null(xlim)) rng[2] = max(xlim[2], rng[2])

  # set bins
  breaks = seq(rng[1], rng[2], length = n_bins)

  # calculate the data for the histogram
  prior_hist = hist(prior_samps_keep, plot = FALSE, breaks = breaks)
  post_hist = hist(post_samps_keep, plot = FALSE, breaks = breaks)

  # convert bin counts to probabilities
  # account for fraction not shown
  prior_probs = prior_hist$counts/sum(prior_hist$counts) * p_prior_keep
  post_probs = post_hist$counts/sum(post_hist$counts) * p_post_keep

@@

  # draw segments to connect axes at origin
  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
  segments(usr[1], usr[3], usr[1], usr[4], xpd = TRUE)

  # add a legend in the desired location if not NULL
  if (!is.na(legend_loc)) {
    legend(legend_loc, legend = c("Prior", "Posterior"), bty = "n", pch = 22, pt.cex = 1.75, cex = 0.8, col = c(prior_col, post_col), pt.bg = scales::alpha(c(prior_col, post_col), 0.5))
  }

  # if some portion of one of the dists is not shown, include a message
  if (p_post_keep < 1 | p_prior_keep < 1) {
    nice_round = function(x, digits = 2) {
      x_round = round(x, digits = digits)
      if (x_round == 0 & x > 0) x_out  = "<0.01" else x_out = x_round
      x_out
    }

    legend(x = usr[1] - xdiff * 0, y = usr[4] + ydiff * 0.025, xpd = TRUE,
           legend = c(nice_round(1 - p_prior_keep), nice_round(1 - p_post_keep)),
           text.col = c(prior_col, post_col), bty = "n", title.col = "black",
           title = "P Not Shown", cex = 0.8
    )
  }
}
```

```{r post-v-prior-wrappers}
# wrapper to create plot for all populations
post_v_prior_pops = function(post_param, prior_param, legend_loc = "topright", xlim = NULL, is_rho = FALSE, y_max = 0.5, ...) {
